On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2025-02-23 char-4k-bound/char-4k-bound.tex
[4k3] Restore the equation number (12)
[4k3] Fix a theorem number (thanks to the Referee)
[4k3] Omit the redundant condition of semi-general condition (thanks to the Referee)

\begin{lemma}
	\cite[Theorem 3.10]{my-pps-linear-bound-2019}
	\label{lem:no_distance_one}
	Each set $M\in\mathfrak{M}_n$
	such that for some $M_1,M_2 \in M$ equality $|M_1 M_2|=1$ holds,
	consists of $n-1$ points, including $M_1$ and $M_2$, on a straight line,
	and one point out of the line, on the perpendicular bisector of line segment $M_1 M_2$.
\end{lemma}

@@

\begin{theorem}[The Weeding Theorem I]
	\label{thm:weeding_I}
	Let $M = \{M_1, M_2, M_3\} \in \mathfrak{M}_3$ be an IPS of semi-general position with a characteristic different from $4k+3$, $k \in \mathbb{N}_0$. Then, the length of the edge $M_1 M_2$ and its $n$-th Erdős curve, which contains the point $M_3$, have the same parity.
\end{theorem}

@@

\begin{theorem}[The Weeding Theorem II]
	\label{thm:weeding_II}
	Let an IPS in semi-general position $M=\{M_1, M_2, M_3\}\in{\mathfrak{M}_{3}}$ have an even edge length $|M_1 M_2|$, and let point $M_3$ lie on an odd Erdős curve of edge $M_1 M_2$.
	Then the set $M$ has characteristic $p=8k+7$, $k\in \mathbb{N}_{0}$.
\end{theorem}

@@

\begin{eqnarray}
\label{d}
\overline{d}(2,3)&=& 1,{}\nonumber\\
\overline{d}(2,4)&=& 4,{}\nonumber\\
\overline{d}(2,5)&=&  \overline{d}(2,6)= 8,{}\nonumber\\
\overline{d}(2,7)&=& 33,{}\nonumber\\
\overline{d}(2,8)&=&  \overline{d}(2,9)= 56,{}\nonumber\\
\overline{d}(2,10)&=& ... =\overline{d}(2,12)= 105,{}\nonumber\\
\overline{d}(2,13)&=&  \overline{d}(2,14)= 532,{}\nonumber\\
\overline{d}(2,15)&=&  ... = \overline{d}(2,18) = 735,{}\nonumber\\
\overline{d}(2,19)&=& ... = \overline{d}(2,24) = 1995,{}\nonumber\\
\overline{d}(2,25)&=&  ... = \overline{d}(2,27)= 9555,{}\nonumber\\
\overline{d}(2,28)&=& 10672,{}\nonumber\\
\overline{d}(2,29)&=&  ... = \overline{d}(2,36) = 13975,{}\nonumber\\
\overline{d}(2,37) &>& 20\ 000.
\end{eqnarray}

Now we are finally ready to proof our main result.
It improves the bound~\eqref{eq:chebsb_lower_bound}
in our special case.

>>>>

\begin{lemma}
	\cite[Theorem 5.9]{my-pps-linear-bound-2019}
	\label{lem:no_distance_one}
	Each set $M\in\mathfrak{M}_n$
	such that for some $M_1,M_2 \in M$ equality $|M_1 M_2|=1$ holds,
	consists of $n-1$ points, including $M_1$ and $M_2$, on a straight line,
	and one point out of the line, on the perpendicular bisector of line segment $M_1 M_2$.
\end{lemma}

@@

\begin{theorem}[The Weeding Theorem I]
	\label{thm:weeding_I}
	Let $M = \{M_1, M_2, M_3\} \in \mathfrak{M}_3$ be an IPS with a characteristic different from $4k+3$, $k \in \mathbb{N}_0$. Then, the length of the edge $M_1 M_2$ and its $n$-th Erdős curve, which contains the point $M_3$, have the same parity.
\end{theorem}

@@

\begin{theorem}[The Weeding Theorem II]
	\label{thm:weeding_II}
	Let an IPS $M=\{M_1, M_2, M_3\}\in{\mathfrak{M}_{3}}$ have an even edge length $|M_1 M_2|$, and let point $M_3$ lie on an odd Erdős curve of edge $M_1 M_2$.
	Then $\operatorname{char} M=8k+7$, $k\in \mathbb{N}_{0}$.
\end{theorem}

@@

\begin{equation}
	\begin{array}{rcl}
		\label{d}
		\overline{d}(2,3)&=& 1,{}\\
		\overline{d}(2,4)&=& 4,{} \\
		\overline{d}(2,5)&=&  \overline{d}(2,6)= 8,{} \\
		\overline{d}(2,7)&=& 33,{} \\
		\overline{d}(2,8)&=&  \overline{d}(2,9)= 56,{} \\
		\overline{d}(2,10)&=& ... =\overline{d}(2,12)= 105,{} \\
		\overline{d}(2,13)&=&  \overline{d}(2,14)= 532,{}\\
		\overline{d}(2,15)&=&  ... = \overline{d}(2,18) = 735,{} \\
		\overline{d}(2,19)&=& ... = \overline{d}(2,24) = 1995,{} \\
		\overline{d}(2,25)&=&  ... = \overline{d}(2,27)= 9555,{} \\
		\overline{d}(2,28)&=& 10672,{} \\
		\overline{d}(2,29)&=&  ... = \overline{d}(2,36) = 13975,{} \\
		\overline{d}(2,37) &>& 20\ 000.
	\end{array}
\end{equation}

Now we are finally ready to proove our main result.
It improves the bound~\eqref{eq:chebsb_lower_bound}
in our special case.
